Pillar 2 - Topic Modeling

### 2019-04-02 Pillar_2_-_Topic_Modeling.Rmd
very old topic models

COMMENTS: 
Q. Jerry -> For preprocessing (selecting vocabulary), how do we assign words that appear in only one document to a topic? Does it make sense to remove them?

```{r setup, include = T}
knitr::opts_chunk$set(cache.path = "Cache/Pillar 2/")
```

```{r library, message = F}
library(tidyverse)
library(tidytext)

library(ggwordcloud) # Word Clouds
library(topicmodels)
library(lemon)
library(ggthemes)
library(rlang)
library(ldatuning) # ideal number of topics in LDA
```

@@

# Setup
We load the environment `output/data_pillar_2.RDATA`. It contains the list `d_text`, and the datasets `d_course` and `d_transcript`.
```{r import data}
load("output/data_pillar_2.RDATA")

# Only keep course descriptions and overviews from most recent year
d_description <- d_description %>%
  filter(
    `Academic Year` == "2018-2019"
  )

d_overview <- d_overview %>%
  filter(
    `Academic Year` == "2018-2019"
  )
```

@@

# LDA

```{r my_cast_tdm}
my_cast_tdm <- function(data, level) data %>%
  count(`Course ID`, word) %>%
  cast_dtm(`Course ID`, word, n)

@@

## Ideal Number of Topics (RUN ON UM COMPUTER)

```{r controls}
my_control <- list(

  nstart = 10,
  seed   = 1 : 10,
  best   = TRUE,

  burnin = 500,
  iter   = 2000,
  thin   = 100

@@

```{r function my_FindTopicsNumber }
my_FindTopicsNumber <- function(data_cast, n_topics){

@@

  dtm = data_cast,
  topics = n_topics,
  metrics = c("Griffiths2004", "CaoJuan2009", "Arun2010", "Deveaud2014"),
  method = "Gibbs",
  control = my_control,
  mc.cores = 1L

@@

```{r description topics, cache = TRUE}
start.time <- Sys.time()

result_description <- d_description_cast %>% my_FindTopicsNumber(n_topics = seq(from = 5, to = 100, by = 1))

@@

save(result_description,
     file = "Output/LDA_ntopics_description.RDATA")

@@

```{r overview topics, cache = TRUE}
start.time <- Sys.time()

result_overview <- d_overview_cast %>% my_FindTopicsNumber(n_topics = seq(from = 5, to = 100, by = 1))

@@

```{r manual topics, cache = TRUE}
start.time <- Sys.time()

result_manual <- d_manual_cast %>% my_FindTopicsNumber(n_topics = seq(from = 5, to = 155, by = 10))

@@

```{r LDA number topics plot}

load("Output/LDA_ntopics_description.RDATA")

load("Output/LDA_ntopics_overview.RDATA")

load("Output/LDA_ntopics_manual.RDATA")

result_description %>%
  select(-Griffiths2004) %>%
  FindTopicsNumber_plot

result_overview %>%
  select(-Griffiths2004) %>%
  FindTopicsNumber_plot

result_manual %>%
  select(-Griffiths2004) %>%
  FindTopicsNumber_plot

@@

## Fitting Model

```{r LDA fit, cache = TRUE}
n_topics <- 5
levels   <- c("description", "overview", "manual")
list_nam <- character(0)

for(level in levels){

  dataset   <- get(paste("d", level, "cast", sep = "_"))

  LDA_model <- LDA(
    x       = dataset,
    k       = n_topics,
    method  = "Gibbs",
    control = list(
      nstart  = 10,
      seed    = c(1:10),
      best    = TRUE,

      burnin  = 4000,
      iter    = 5000,
      thin    = 500,

      verbose = 1e3,
      save    = 1e3,
      keep    = 1e3)
    )

  nam <- paste("LDA", level, n_topics, sep = "_")

  assign(
    x     = nam,
    value = LDA_model
  )

  list_nam <- c(list_nam, nam)

@@

save(list = list_nam,
     file = "LDA.RDATA")
```

## Visualization
### Functions
```{r LDA prepare, eval = F}
prepare_data_LDA_beta <- function(results){

  tidy(results, matrix = "beta") %>%
    mutate(topic = paste("Topic", topic)) %>%
      group_by(topic) %>%
        top_n(10, beta) %>%
      ungroup %>%
      arrange(topic, desc(beta))

@@

prepare_data_LDA_gamma <- function(results, level = Course){

  data_gamma <- tidy(results, matrix = "gamma") %>%
    mutate(topic = paste("Topic", topic)) %>%
    rename(`Course ID` = document)

>>>>

```{r setup, include = FALSE}
knitr::opts_chunk$set(cache.path = "Cache/Pillar 2/",
                      eval = FALSE)
```

```{r library, message = FALSE, eval = TRUE}
library(tidyverse)
library(tidytext)

library(ggwordcloud) # Word Clouds
library(topicmodels)
library(lemon)
library(ggthemes)
library(rlang)
library(ldatuning) # ideal number of topics in LDA

library(modelr) #cross_validation
```

@@

# Setup
We load the environment `output/data_pillar_2.RDATA`. It contains the data sets:
`d_AoD`, `d_assessment`, `d_course`, `d_description`, `d_manual`, `d_overview`, `d_transcript`, and a list `lists`.
For `d_description` and `d_overview`, we keep only the most recent year.
```{r import data, eval = TRUE}
load("output/data_pillar_2.RDATA")

# Only keep course descriptions and overviews from most recent year
d_text <- d_text %>% map(function(tb, y) tb %>% filter(year == max(year)))
```

@@

# LDA
The function `my_cast_tdm` casts our dataframes into a tdm.
```{r my_cast_tdmxxxxx}
my_cast_tdm <- function(data, level) data %>%
  count(`Course ID`, word) %>%
  cast_dtm(`Course ID`, word, n)

@@

## Ideal Number of Topics (RUN ON UM COMPUTER)
To decide the number of topics to discover, we run (four) three different tests.

First we set the control for the test.
```{r controls, eval = TRUE}
my_control <- list(

  nstart = 20,
  seed   = 1 : 20,
  best   = TRUE,

  burnin = 1000,
  iter   = 15000,
  thin   = 100

@@

```{r fast control}
my_control_fast <- list(

  nstart = 1,
  seed   = 1,
  best   = TRUE,

  burnin = 5,
  iter   = 10,
  thin   = 2

###With Package built in Function
The function `my_FindTopicsNumber` builds a Topic Model and applies the measurements 
```{r function my_FindTopicsNumber }
my_FindTopicsNumber <- function(data_cast, n_topics){

@@

  dtm = data_cast,
  topics = n_topics,
  metrics = c("CaoJuan2009", "Arun2010", "Deveaud2014"),
  method = "Gibbs",
  control = my_control,
  mc.cores = 4L

@@

}
```
We run the test for descriptions, documenting the duration (starting_time - ending_time). We build 95 models (5 to 100 in increments of 1).
```{r description topics, cache = TRUE}
start.time <- Sys.time()

result_description <- d_description_cast %>% my_FindTopicsNumber(n_topics = seq(from = 5, to = 100, by = 2))

@@

save(result_description,
     file = "Output/LDA_ntopics.RDATA")

@@

We run the test for overview, documeting its duration. 
```{r overview topics, cache = TRUE}
start.time <- Sys.time()

result_overview <- d_overview_cast %>% my_FindTopicsNumber(n_topics = seq(from = 5, to = 100, by = 2))

@@

We run the test for manuals, documenting its duration.
```{r manual topics, cache = TRUE}
start.time <- Sys.time()

result_manual <- d_manual_cast %>% my_FindTopicsNumber(n_topics = seq(from = 5, to = 75, by = 5))

@@

We examine the result of the experiment by plotting them on a graph.
```{r LDA number topics plot}

load("Output/LDA_ntopics.RDATA")

result_description %>%
  FindTopicsNumber_plot

result_overview %>%
  FindTopicsNumber_plot

result_manual %>%
  FindTopicsNumber_plot

```
From the results we see that the ideal number of topics is somewhere between 35 and 40.

## Fitting Model
The function `my_cast_tdm` casts our dataframes into a tdm.
```{r my_cast_tdm, eval = TRUE}
my_cast_tdm <- function(data) data %>%
  count(`Course ID`, word) %>%
  cast_dtm(`Course ID`, word, n)

d_cast <- d_text %>% map(my_cast_tdm)

The function `my_LDA` fits an LDA model on the DTM using the previous controls.
```{r my_LDA, eval= TRUE}

#my_LDA
my_LDA <- function(n_topics, corpus, control = my_control){

  LDA_model <- LDA(
    x       = corpus,
    k       = n_topics,
    method  = "Gibbs",
    control = control
    )
}

@@

Next we train our model with different number of topics.
```{r LDA fit, cache = TRUE, eval = TRUE}
topic_model <- tibble(

  n_topic = seq(from = 5, to = 250, by = 5)

  ) %>%

  mutate(
    TM_overview = n_topic %>% map( .f = my_LDA, corpus = d_cast$overview),
    TM_manual   = n_topic %>% map( .f = my_LDA, corpus = d_cast$manuals)
  )
```

##Model Evaluation
###Perplexity
Perplexity is a measure of how well a probability model predicts a sample. Thus we need to do cross validation. 
```{r perplexity function, eval = TRUE}

#perplexity Function
my_perplexity <- function(model, d_cast){
  perplexity(model, d_cast, estimate_theta = FALSE)
}

#Get perplexity
test_perplexity <- topic_model %>%
  mutate(perplex_overview = map(.x = TM_overview, .f = my_perplexity, d_cast$overview),
         perplex_manual   = map(.x = TM_manual,   .f = my_perplexity, d_cast$manual))
```

###log_likelihood
```{r log likelihood, eval = TRUE}
# #my_loglikelihood function
# my_loglike <- function(model){
#   return(model@loglikelihood)
# }
# 
# #get loglikelihood
# test2 <- topic_test %>% mutate(loglike_overview    = map(.x = TM_overview, .f = my_loglike),
#                                   loglike_manual   = map(.x = TM_manual,   .f = my_loglike))

#Log likelihood:
test_likelihood <- topic_test %>% mutate(logLik_overview = map(.x = TM_overview, .f = logLik),
                               logLik_manual   = map(.x = TM_manual,   .f = logLik))

###Plots
```{r perplexity plots, eval = TRUE}
#perplexity
plot(topic_test$n_topic, topic_test$perplex_overview)
plot(topic_test$n_topic, topic_test$perplex_manual)

#log likelihood
plot(test3$n_topic, test3$logLik_overview)
plot(test3$n_topic, test3$logLik_manual)
```

##Get Beta/Gamma functions
```{r getting gamma and beta, eval = TRUE}
get_beta <- function(results){

  tidy(results, matrix = "beta")           %>%
    mutate(topic = paste("Topic", topic) ) %>%
      arrange(topic, desc(beta) )

@@

get_gamma <- function(results){

  tidy(results, matrix = "gamma")          %>%
    mutate(topic = paste("Topic", topic) ) %>%
      arrange(topic, desc(gamma) )
}

##Apply beta and gamma
```{r applying get_gamma and get_beta, eval = TRUE}
topic_model_gb <- topic_model %>%
  transmute(
    n_topic    = n_topic,
    g_overview = TM_overview %>% map( .f = get_gamma),
    g_manual   = TM_manual   %>% map( .f = get_gamma),
    b_overview = TM_overview %>% map( .f = get_beta),
    b_manual   = TM_manual   %>% map( .f = get_beta)
      )
```
##Saving filed for different sessions
```{r saving, eval = TRUE}
save(topic_model_gb, 
     file = "Output/topic_model_gb.RDATA")
```
#Distributions
#NOTE: We need to select how many topics to use
##Distributions of best models
```{r Distributions, eval = FALSE}
#select number of topics
n_topics_overview <- 36
n_topics_manual   <- 40

#Crop models
TM_overview <- topic_model_gb %>%
  filter(n_topic== n_topics_overview)

TM_manual   <- topic_model_gb %>%
  filter(n_topic== n_topics_manual)

#Distributions
distribution <- list()

distribution$beta$overview  <- TM_overview %>% pull(b_overview)
distribution$beta$manual    <- TM_manual   %>% pull(b_manual)

distribution$gamma$overview <- TM_overview %>% pull(g_overview)
distribution$gamma$manual   <- TM_manual   %>% pull(g_manual)

```
##Inspect topics
THE TOPICS ARE SUPPER STRANGE!
```{r inspect topics, eval = FALSE}

inspect_topics <- function(d_beta){
  data.frame(d_beta) %>%
    group_by(topic) %>%
    top_n(10, beta)

@@

topics <-  lapply(
  distribution$beta,
  inspect_topics
)
```
#App
##Selectig keywords
```{r key words}
get_top_words <- function(d_beta, n = 5){
  data.frame(d_beta) %>%
    group_by(topic) %>%
    top_n(n, beta) %>%
    pull(term)%>%
    unique
}

kw <- lapply(
  distribution$beta,
  get_top_words
)
```
####TEMPORTARY: stopwords for keywords
This section is for presentations
```{r stopwords for kw}
#kw$overview
not_include <- c("source", "primary", "type", "assess", "involve", "e.g", "discussion", "institute", "ha", "introduce",
                 "role","address", "student", "examination","coordinator", "maastrichtuniversity.nl", NA, "identify", "manner", "mechanism", "concept", "hour", "teach",  "depth","question", "specific", "busy","academic", "semester", "week", "test", "session", "team", "communicate", "theory", "text", "library", "article", "examine", "current", "routledge", "temporary", "flow", "level", "study")

remove_words <- function(x){
  setdiff(x, not_include)
}

kw1 <- lapply(
  kw,
  remove_words
)

```
##Convenience vectors for APP
```{r for convenience}
# set seed
set.seed(1)

#
## All courses
course_all <- d_course %>%
  inner_join(
    d_transcript,
    by = "Course ID"
  ) %>%
  distinct(
    `Course ID`
  ) %>%
  # remove semester abroad, skills and projects
  filter(
    ! str_detect(`Course ID`, pattern = "SA|SKI|PRO")
  ) %>%
  pull

#
##courses following_semester
course_following_semester <- sample(
  x       = course_all,
  size    = 60,
  replace = FALSE
  ) %>% sort
```
## Saving files for APP
```{r app files}
save(distribution, kw, course_all, course_following_semester,
     file = "App/Recommender System/data_topic_models.RDATA")
```

# Visualization
### Functions 
This part is adapted 
```{r LDA prepare, eval = F}
prepare_data_LDA_beta <- function(d_beta){

  data.frame(d_beta) %>%
    mutate(topic = paste("Topic", topic)) %>%
      group_by(topic) %>%
        top_n(10, beta) %>%
      ungroup %>%
      arrange(topic, desc(beta))

} #repetition??? of inspect topics?

prepare_data_LDA_gamma <- function(d_gamma, level = Course){

  data_gamma <- data.frame(d_gamma) %>%
    mutate(topic = paste("Topic", topic)) %>%
    rename(`Course ID` = document)
